### 2014-09-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Update HRR details

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor_Metric}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor_Metric}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Metric}
\caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure. Stairs and rooms are identified using measurements collected by NIST.}
\label{fig:floor_plan}
\end{figure}

@@

\begin{lstlisting}
&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Fire_Ramp' /
&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER' /

&SURF ID='FLASHOVER_BURNER', HRRPUA=270.563, COLOR='RED' /
&VENT XB=0.0, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
&DEVC ID='TIMER_FLASHOVER', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.FALSE., SETPOINT=300 /
\end{lstlisting}
Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.

>>>>

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor_Metric}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor_Metric}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Metric}
\caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure. The fire originated in the living room on the basement floor. Stairs and rooms are identified using measurements collected by NIST.}
\label{fig:floor_plan}
\end{figure}

@@

\begin{lstlisting}
&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Fire_Ramp' /
&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER', DEVC_ID='TIMER_INITIAL_BURNER_OFF' /
&DEVC ID='TIMER_INITIAL_BURNER_OFF', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.TRUE., SETPOINT=300 /

&SURF ID='FLASHOVER_BURNER', HRRPUA=365.097, COLOR='RED' /
&VENT XB=0.1, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
&DEVC ID='TIMER_FLASHOVER', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.FALSE., SETPOINT=300 /
\end{lstlisting}
Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
